Optimal (Multiway) Spatial Joins

### 2024-06-01 5.2.tex
5.2

Next, we will show that $r_{k-2}\in \contained_{R_{k-2}}(\bm{t})$. As proven above, $B_\bm{t} = h'\cap v = p$. Recall that $p = (x,y)$. We can denote the effective horizontal segment of $\bm{t}$ as $[x_1, x] \times y$. Then, we only need to prove that $[x_1,x] \subseteq [\xleft(r_2), \xright(r_2)]$ and $y \in [\ybot(r_2), \ytop(r_2)]$. Since $r_{k-2}$ is a left-end covering rectangle of $h$, we have  $x_1 \in [\xleft(r_2), \xright(r_2)]$ and $y \in [\ybot(r_2), \ytop(r_2)]$. As we show in the last paragrah, $r_{k-2}$ also covers $p$. Therefore, $x \in [\xleft(r_2), \xright(r_2)]$, and $[x_1,x] \subseteq [\xleft(r_2), \xright(r_2)]$. Hence, $r_{k-2}\in \contained_{R_{k-2}}(\bm{t})$.

>>>>

Next, we aim at proving $r_{k-2}\in \contained_{R_{k-2}}(\bm{t})$. As proven above, $h'\cap v= p$. In another word, $B_\bm{t} = p$. Recall that we defind $p = (x,y)$, and $h' = [x_1,x_2']\times y$. Thus, we can denote the effective horizontal segment of $\bm{t}$ as $[x_1, x] \times y$. For our goal, we only need to show that $[x_1,x] \subseteq [\xleft(r_2), \xright(r_2)]$ and $y \in [\ybot(r_2), \ytop(r_2)]$. 
\begin{itemize}
    \item Since $r_{k-2}$ is a left-end covering rectangle of $h$, we have  $x_1 \in [\xleft(r_2), \xright(r_2)]$. As we show in the last paragrah, $r_{k-2}$ also covers $p$, whose x-coordinate, denoted as $x$, satisfies $x_1 \le x$. Therefore, $x \in [\xleft(r_2), \xright(r_2)]$, and $[x_1,x] \subseteq [\xleft(r_2), \xright(r_2)]$.
    \item The y-coordinate of $h$ is $y$. Since $r_{k-2}$ intersects $h$, $y \in [\ybot(r_2), \ytop(r_2)]$.
\end{itemize}
